---
title: "finalproject"
author: "George Oberle"
date: "October 28, 2014"
output: html_document
---

```{r}
vavotes<- read.csv("~/CLIO-3/New Nation Votes data files/va-votes.tsv",
                   sep = "\t", stringsAsFactors = FALSE)
```

# Followed directions in chapter until line 139

```{r}
library (rgdal)
setwd("~/CLIO-3/finalproject")
map_sp <- readOGR("nhgis-shp/", "state_1850")
class(map_sp)
str(map_sp, max.level = 2)
map_sp@bbox
map_sp@proj4string
head(map_sp@data)
plot(map_sp)
earth <- readOGR("~/CLIO-3/natural_earth_vector/50m_physical/ne_50m_land/", "ne_50m_land")
plot(earth, col = "gray")
title("The world according to EPSG 4326")
winkel <- spTransform(earth, CRS("+proj=wintri"))
plot(winkel, col = "gray")
title("The world according to Oswald Winkel")

library (sp)
class(map_sp)


map_sp
class(map_sp)
str(map_sp, max.level = 2)
map_sp@bbox
map_sp@proj4string
head(map_sp@data)
plot(map_sp)
earth <- readOGR("data/ne_50m_land/", "ne_50m_land")
plot(earth, col = "gray")
title("The world according to EPSG 4326")
winkel <- spTransform(earth, CRS("+proj=wintri"))
plot(winkel, col = "gray")
title("The world according to Oswald Winkel")
```






```

```{r}
library (ggplot2)
library (ggmap)
geocode("San Francisco, CA")
geocode("San Francisco, CA", output = "more")

cities <- data.frame(name = c("Saint Louis, MO",
                    "San Francisco, CA",
                    "Boston, MA",
                    "Charleston, SC",
                    "Houston, TX"),
           stringsAsFactors = FALSE)

cities_geocoded <- geocode(cities$name)
cities <- cbind(cities, cities_geocoded)

library(ggplot2)
ggplot(cities, aes(x = lon, y = lat)) +
  geom_point() +
  geom_text(aes(label = name), vjust = -1) +
  coord_map()
# why is the gis join arguement best to use?
map_df <- fortify(map_sp, region = "GISJOIN")
head(map_df)

map_1850 <- ggplot() + 
  geom_map(data = map_df,
           map = map_df,
           aes(x = long, y = lat, group = group, map_id = id),
           fill = "white",
           color = "black",
           size = 0.2) +
  coord_map() +
  theme_minimal()

map_1850


map_1850 +
  geom_point(data = cities, aes(x = lon, y = lat),
             color = "red", size = 3) +
  geom_text(data = cities, aes(x = lon, y = lat, label = name),
            vjust = -1)


library(dplyr)

library(historydata)
data(paulist_missions)
glimpse(paulist_missions)

map_1850 +
  geom_point(data = paulist_missions,
             aes(x = long, y = lat, size = confessions),
             color = "red", shape = 1) +
  theme(legend.position = "bottom") +
  scale_size(range = c(2, 8)) + 
  ggtitle("Paulist missions as points")

map_1850 +
  geom_hex(data = paulist_missions,
             aes(x = long, y = lat)) +
  theme(legend.position = "bottom") +
  ggtitle("Paulist missions with hex bin")

map_1850 +
  geom_density2d(data = paulist_missions,
             aes(x = long, y = lat)) +
  theme(legend.position = "bottom") +
  ggtitle("Paulist missions with density plot")

```

```{r}
library(historydata)
data(early_colleges)
glimpse(early_colleges)

geocode 


map_1850 +
  geom_point(data = early_colleges,
             aes(x = established, y = ),
             color = "red", shape = 1) +
  theme(legend.position = "bottom") +
  scale_size(range = c(2, 8)) + 
  ggtitle("Early Colleges as points")

```

```{r}
library (historydata)
data(early_colleges)
glimpse (early_colleges)
summarize(early_colleges, city + State)
          %>%
  

> library(dplyr)
> library(tidyr)


> library(early_colleges)
> library(stringr)

            
head(early_colleges)
str(early_colleges)
str(early_colleges)


 

```

